
---
title: "Sabrina Carpenter"
author: "Alida Plas"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
---

# Introduction Portfolio

PLEASE DO NOT SHOW THIS PORTFOLIO IN CLASS
The collection of music that I would like to learn more about are the songs of Sabrina Carpenter. I choose this artist, because I have been listening to her music for 7 years now. I grew up with her, but she also did and her music has changed a lot over time. Sabrina’s first single ‘Can’t Blame a Girl for Trying’ came out in March 2014 when she was 14 years old. She is now 22 and in the mean time she released four albums and many singles. 
So my comparison points will be the different albums of Sabrina Carpenter. Her first album, ‘Eyes Wide Open’, which talks about love and teenage problems, has a pop sound with a bit of folk. The production mainly consists of guitars, piano and drums. Her last album ‘Singular: Act II’, released in 2019, is a dance, pop and R&B record. In general, she discusses self-reflection and self-discovery. So both in style and theme there is already a difference.
What I would like to find out is how her music has changed over the years. Has anything stayed the same during that time and what has changed? You can hear a difference, but where exactly is it?
A song that is atypical is ‘Skinny Dipping’. It is one of her recent singles, which will be part of her new coming album. In this song she mainly talks and describes an imaginary world. She starts singing in the pre-chorus, but the narrative part is accompanied with an instrumental background. 

```{r include = FALSE}
library(flexdashboard)
library(tidyverse)
library(spotifyr)
library(usethis)
library(compmus)
library(datasets)
library(compmus)
```
---

# Valence over time

***
When I listen to the various albums of Carpenter myself, I hear that her first album is clearly 'more cheerful' than her last. But what does Spotify say about this. The API called valence, describes the musical positiveness conveyed by a track.
The order of the albums is: 'Eyes Wide Open' (EWO), 'EVOLution' (EVOL), 'Singular Act I' (SAI) and 'Singular Act II' (SAII).
Sabrina's first album, which is also described as upbeat, has the highest maximum. Which therefore fits what you can hear.
Singular act I and II both belong to 1 project, but were released separately due to the difference in lyrical content. Act I is an album full of self-confidence, while Act II is filled with feelings and emotions. In the box plot you see that the average of the positiveness is much lower with Act I than the album in which many emotional things are also discussed. This is mainly because text is not included, but it is an interesting observation. Because with your ear, you would have judged it differently. The median of SAI and SAII are in the same place. The middle value of both albums is equal. Singular Act II also has a few outliers. 'Tell em' has a valence of 0.199, 'Exhale' 0.276 and 'Take Off All Your Cool' 0.809. I myself was surprised at the result of 'Take Off All Your Cool' and wonder what other people think of this API score from Spotify.
You also see that the box of EVOL and SAII barely overlap. This also means that the difference between the two is the greatest. The valence at SAII is higher on average. Evolution's tracks sound more sad, depressed and angry. SAII's tracks sound the most cheerful, cheerful and euphoric.
Over the years, the valence has been very varied.

##

```{r}
EWO <- get_playlist_audio_features("","2PUT9OaUA6eODR3et4CFXB") 
EVOL <- get_playlist_audio_features("","6wLxOjmHS2ojcXLlgSnfNB")
SAI <- get_playlist_audio_features("","3bEVrN4e4ZZT3abT0qvLTh")
SAII <- get_playlist_audio_features("","0ajsJz4w31SYpdGObMUZQ8")

Album <-
  bind_rows(
    EWO %>% mutate(category = "EWO"),
    EVOL %>% mutate(category = "EVOL"),
    SAI %>% mutate(category = "SAI"),
    SAII %>% mutate(category = "SAII")
  )

Album %>%
  ggplot(aes(x = category, y = valence)) +
  geom_boxplot()

```

---
# Oldest vs. newest single

***
A few weeks ago, Carpenter released her latest single called 'Fast Times'. Compared to her first single, the style is completely different. The purpose of this page is therefore to compare her first single, which was released on March 14, 2014, 'Can't Blame a Girl for Trying', with her last single, which was released on February 18, 2022.
In the chromagram of Fast Times we can clearly see how the song is built and how certain parts come back. The first small block is the intro, this runs to about 10 seconds. Then the verse starts which is actually built on the intro, so it's light blue. It's very similar. In the 3 block, around 25 seconds, there is a modulation that you see again. Yet the first part is all very similar which makes it a big block. After that comes a block with a lot of yellow, this means that it is very different. Which is also true because this is where the chorus starts. Then follows the block of the verse. Followed by 2 times the chorus. A cross is created there, through the bridge. And then the chorus again twice.
The chromagram of ‘Can't Blame a Girl for Trying shows less structure’. Everything looks the same. So you can say that the latest single has more of a structure and structure with clear differences. 
I also want to compare timbre. But haven't been able to get the formula to work yet. He does not recognize the Compmus of timbre, but that of pitches. Does anyone have an idea where it could be wrong?

## Can't Blame a Girl for Trying

```{r}
CBaGfT <-
  get_tidy_audio_analysis("5K7fGxZQB0K5sPKhLe9e07") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

compmus_long_distance(
  CBaGfT %>% mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  CBaGfT %>% mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "manhattan"
) %>%
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Can't Blame a Girl for Trying", y = "") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
```

## Fast Times

```{r}
FastTimes <-
  get_tidy_audio_analysis("0oN3KzKOxYtyIuNiobf8Q4") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

compmus_long_distance(
  FastTimes %>% mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  FastTimes %>% mutate(pitches = map(pitches, compmus_normalise, "chebyshev")),
  feature = pitches,
  method = "cosine"
) %>%
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_equal() +
  labs(x = "Fast Times", y = "") +
  theme_minimal() +
  scale_fill_viridis_c(guide = NULL)
```

