
---
title: "Sabrina Carpenter"
author: "Alida Plas"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

# Introduction Portfolio

PLEASE DO NOT SHOW THIS PORTFOLIO IN CLASS
The collection of music that I would like to learn more about are the songs of Sabrina Carpenter. I choose this artist, because I have been listening to her music for 7 years now and I am a big fan. I grew up with her, but she also did and her music has changed a lot over time. Sabrina’s first single ‘Can’t Blame a Girl for Trying’ came out in March 2014 when she was 14 years old. She is now 22 and in the mean time she released four albums and many singles. 
So my comparison points will be the different albums of Sabrina Carpenter. Her first album, ‘Eyes Wide Open’, which talks about love and teenage problems, has a pop sound with a bit of folk. The production mainly consists of guitars, piano and drums. Her last album ‘Singular: Act II’, released in 2019, is a dance, pop and R&B record. In general, she discusses self-reflection and self-discovery. So both in style and theme there is already a difference.
What I would like to find out is how her music has changed over the years. Has anything stayed the same during that time and what has changed? You can hear a difference, but where exactly is it?
A song that is atypical is ‘Skinny Dipping’. It is one of her recent singles, which will be part of her new coming album. In this song she mainly talks and describes an imaginary world. She starts singing in the pre-chorus, but the narrative part is accompanied with an instrumental background. 

```{r include = FALSE}
library(flexdashboard)
library(tidyverse)
library(spotifyr)
library(usethis)
library(compmus)
library(datasets)
```
---

# Valence over time

```{r}
EWO <- get_playlist_audio_features("","2PUT9OaUA6eODR3et4CFXB") 
EVOL <- get_playlist_audio_features("","6wLxOjmHS2ojcXLlgSnfNB")
SAI <- get_playlist_audio_features("","3bEVrN4e4ZZT3abT0qvLTh")
SAII <- get_playlist_audio_features("","0ajsJz4w31SYpdGObMUZQ8")

Album <-
  bind_rows(
    EWO %>% mutate(category = "EWO"),
    EVOL %>% mutate(category = "EVOL"),
    SAI %>% mutate(category = "SAI"),
    SAII %>% mutate(category = "SAII")
  )

Album %>%
  ggplot(aes(x = category, y = valence)) +
  geom_boxplot()

```

---
# Chroma

```{r}
SkinnyDipping <-
  get_tidy_audio_analysis("7u6HtmuMeuiVdwwFul5xHi") %>%
  select(segments) %>%
  unnest(segments) %>%
  select(start, duration, pitches)

SkinnyDipping %>%
  mutate(pitches = map(pitches, compmus_normalise, "euclidean")) %>%
  compmus_gather_chroma() %>% 
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = pitch_class,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  theme_minimal() +
  scale_fill_viridis_c()
```
